\bf A simple algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
big refactor

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
%\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}

@@

%\usepackage[section]{placeins}
\usepackage{subfigure}

@@

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}

\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}{Remark}
\newtheorem{fact}{Fact}

@@

\author{
Elvis DOHMATOB
\\
Parietal team, Inria Saclay Ile-de-France, Saclay, France\\
\textit{email}: elvis.dohmatob@inria.fr}

\title{\bf Primal-dual algorithm for computing Nash equilibria in
% two-person zero-sum
sequential games with imcomplete information
% with imcomplete information and perfect recall
}

@@

\begin{abstract}
We present a simple primal-dual algorithm
%with low costs per iteration,
for computing Nash-equilibria in two-person zero-sum sequential games
with imcomplete information and perfect recall (like Texas Hold'em
Poker). This primal-dual algorithm derives from the general
primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010,chambolle2014ergodic}. It should be noted that
the latter primal-dual algorithm is not directly applicable to compute
Nash equilibria for the aforementioned games considered here since the
strategy profiles of players (polyhedra) are so complex that it is not
possible
% (for example, simplexes for simultaneous games, and intersections of
% hyperplanes and nonnegative orthants, for sequential games)
 to effectively compute % (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
The core of our technique is to rewrite the equilibrium problem as an
equivalent saddle-point problem for which the proximal operators can
be computed analytically.
 %% dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme.
Our algorithm only performs basic iterations
(i.e iterations involving no
% only involving basic operations like matvec, clipping, etc., and no
calls to external first-order oracles, etc.).
Our algorithm is applicable to a broad class of two-person zero-sum
games including simultaneous games and sequential games with
imcomplete information and perfect recall. The applicability to the
latter kind of games is thanks to the sequence-form representation von
Stengel's \cite{von1996efficient}
%% Unlike the EGT (Excessive Gap Technique) recently used in
%% \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap
%% and constant cost per iteration.
As an application, we apply our algorithm to solve Kuhn 3-card Poker.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

@@

\subsection{Notation and terminology}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$.
%% For example, $((-2, \pi))_+ = (max(-2, 0),
%% max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
denotes the $m$-by-$n$ matrix of zeros.

@@

\subsection{Statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{von1996efficient,vonequilibrium}, where it was established that
for sequential two-person zero-sum games with imcomplete information
and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1
  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
all linear in the size of the game tree (number of states in the game)
and such that Nash equilibria correspond to pairs $(x, y)$ of
\textit{realization plans} which solve the primal LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }e_1^Tp, \hspace{.5em}\text{ subject to }(y,p) \in
     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}

@@

\subsection{Outline of the article}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm for computing Nash $(\rho, \epsilon$)-equilibria for
sequential two-person zero-sum games with imcomplete information and
perfect recall.

@@

The primal-dual algorithm first developed in \cite{chambolle2010} was
proposed \cite{chambolle2014ergodic} in to solve matrix games on
simplexes. It should be stressed that such matrix games are
considerably simpler than the games considered here. Indeed, the
authors in \cite{chambolle2014ergodic} use the fact that computing the
euclidean projection of a point unto a simplex can be done in linear
time as in \cite{duchi2008efficient}. In contrast, no such efficient
algorithm is known nor is likely to exist for the polyhedra $Q_k$
defined in \eqref{eq:polyhedron}, the strategy profiles for players in
the games considered here. It should however be noted that such this
projection can still be done iteratively using, for example, the
algorithm in proposition 4.2 of \cite{combettes2010dualization} or any
CQ algorithm (since this projection sub-problem, is, in fact a
\textit{split-feasibility problem}), for example. Unfortunately, as
with any nested iterative scheme, one would have to solve this
sub-problem with finer and finer precision.

@@

Finally, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
\times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
\begin{eqnarray}
  \left.
  \begin{aligned}
    \hat{\Psi}_1(y, p, x, q) &:=
    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
    p, x, q) := \infty \text{ otherwise}\\
    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(y, p) \text{ if
    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
  \end{aligned}
  \right\}
\end{eqnarray}

Consider the GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$)
  \begin{eqnarray}
    \left.
    \begin{aligned}
      \text{Find }(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}_+
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
  \mathbb{R}^{l_2}\text{ such that }\hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*, q^*)
      \text{ and }\\
      \hspace{.5em}\hat{\Psi}_2(y^*, p^*, x^*, q^*) \le
      \hat{\Psi}_2(y^*, p^*, x, q)
        \forall (y,p, x, q) \in \mathbb{R}^{n_2}_+
      \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
      \mathbb{R}^{l_2}.
    \end{aligned}
    \right\}
    \label{eq:unconstrained_pb}
  \end{eqnarray}
  \label{thm:pd}

@@

\begin{proof}
Define $S_1 := \dom(g_1) = \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$
and $S_2 := \dom(g_2) = 
\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$. Noting that the
equilibria of the LCPs \eqref{eq:primal_pb},
\eqref{eq:dual_pb}, and the equilibria of GSP($\Psi_1$, $\Psi_2$,
$g_1$, $g_2$) are contained in $S_1 \times S_2$, it suffices to show
that at any point $(y, p, x, q) \in S_1 \times S_2$, the duality
primal-dual gap between the primal LCP \eqref{eq:primal_pb} and the
dual LCP \eqref{eq:dual_pb} equals the primal-dual gap of
GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).

Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
$a(x,y)$, can be written as
\begin{eqnarray*}
  \begin{aligned}
    a(y,p) &= e_1^Tp +
    i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
    i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) +
    i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x' \geq
      0}{\text{max}}\text{ }x'^T(Ay - E_1^Tp) +
    \underset{q'}{\text{max}}\text{ }q'^T(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x',
      q'}{\text{max}}\text{ }x'^TAy - x^TE_1^Tp + q'^TE_2y -
    (i_{\mathbb{R}^{n_1}_+}(x') + e_2^Tq)\\
    &= g_1(y,p)
      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
      q') = g_1(y,p) -\phi_2(y,p),
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}

where $\phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') \in [-\infty, +\infty)$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $\phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) \in
         [-\infty, +\infty)$.
Thus, one can compute the primal-dual gap between primal LCP
\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.

@@

Consider the following algorithm
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$
\Ensure $(\rho, \epsilon)$-Nash equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} - \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, we have the ergodic
error bounds
\begin{eqnarray}
\|\tilde{\epsilon}^{a}_k\| \le \rho\text{ and }\|\tilde{v}^{a}_k\| \le
\epsilon, \forall k \ge 2d_0\|K\|max(5d_0/\rho, 1/\epsilon).
\end{eqnarray}

>>>>

\documentclass[envcountsame]{llncs} % For LaTeX2e
%\usepackage{mathpazo}
%\usepackage{nips14submit_e,times}
%\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts}%,amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}

@@

%\usepackage[section]{placeins}
\usepackage[FIGTOPCAP]{subfigure}

@@

%\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}

%\newtheorem{proposition}[theorem]{Proposition}
%% \newtheorem{corollary}[theorem]{Corollary}
%% \newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}{Remark}
\newtheorem{fact}{Fact}

@@

\title{\bf A simple algorithm for computing approximate Nash equilibria in
  two-person zero-sum games with imcomplete information}
\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
\institute{
Parietal team, Inria Saclay Ile-de-France, Saclay, France
}

@@

\begin{abstract}
We present a simple primal-dual algorithm
%with low costs per iteration,
for computing approximate Nash equilibria in two-person zero-sum
sequential games with imcomplete information and perfect recall (like
Texas Hold'em Poker).
Our algorithm only performs basic iterations
(i.e iterations involving no
% only involving basic operations like matvec, clipping, etc., and no
calls to external first-order oracles, etc.) and is applicable to a
broad class of two-person zero-sum
games including simultaneous games and sequential games with
imcomplete information and perfect recall. The applicability to the
latter kind of games is thanks to the sequence-form representation von
Stengel's \cite{von1996efficient}.
%% Unlike the EGT (Excessive Gap Technique) recently used in
%% \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap
%% and constant cost per iteration.
As an application, we apply our algorithm to solve Kuhn 3-card Poker.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

@@

\paragraph{\textbf{Notation and terminology.}}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$.
%% For example, $((-2, \pi))_+ = (max(-2, 0),
%% max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
denotes the $m$-by-$n$ matrix of zeros.

@@

\paragraph{\textbf{Statement of the problem.}}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{von1996efficient,vonequilibrium}, where it was established that
for sequential two-person zero-sum games with imcomplete information
and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1
  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
all linear in the size of the game tree (number of states in the game)
and such that Nash equilibria correspond to pairs $(x, y)$ of
\textit{realization plans} which solve the primal LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }e_1^Tp, \hspace{.5em}\text{ subject to }(y,p) \in
     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}

@@

\paragraph{\textbf{Our contribution.}}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm for computing Nash $(\rho, \epsilon$)-equilibria for
sequential two-person zero-sum games with imcomplete information and
perfect recall.

@@

The primal-dual algorithm first developed in \cite{chambolle2010} was
proposed \cite{chambolle2014ergodic} in to solve matrix games on
simplexes. It should be stressed that such matrix games are
considerably simpler than the games considered here. Indeed, the
authors in \cite{chambolle2014ergodic} use the fact that computing the
euclidean projection of a point unto a simplex can be done in linear
time as in \cite{duchi2008efficient}. In contrast, no such efficient
algorithm is known nor is likely to exist for the polyhedra $Q_k$
defined in \eqref{eq:polyhedron}, the strategy profiles for players in
the games considered here. It should however be noted that such this
projection can still be done iteratively using, for example, the
algorithm in proposition 4.2 of \cite{combettes2010dualization}%%  or any
%% CQ algorithm (since this projection sub-problem, is, in fact a
%% \textit{split-feasibility problem}), for example
. Unfortunately, as
with any nested iterative scheme, one would have to solve this
sub-problem with finer and finer precision.

@@

Finally, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
\times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
\begin{eqnarray}
  \left.
  \begin{aligned}
    \hat{\Psi}_1(y, p, x, q) &:=
    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
    p, x, q) := \infty \text{ else}\\
    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(y, p) \text{ if
    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ else}.
  \end{aligned}
  \right\}
\end{eqnarray}

Define the sets $S_1 := \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$ and $S_2 :=
\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$ and consider the
GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$): Find $(y^*,p^*, x^*, q^*) \in
S_1 \times S_2$ such that
\begin{eqnarray}
  \left.
  \begin{aligned}
    \hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, &p, x^*,
    q^*),\hspace{.5em} \hspace{.5em}\hat{\Psi}_2(y^*, p^*, x^*, q^*)
    \le \hat{\Psi}_2(y^*, p^*, x, q)\\
    &\forall (y,p, x, q) \in S_1 \times S_2.
  \end{aligned}
  \right\}
  \label{eq:unconstrained_pb}
\end{eqnarray}
\label{thm:pd}

@@

\begin{proof}
Note that $\dom(g_1) = S_1$ and $\dom(g_2) = S_2$ and observe that the
equilibria of the LCPs \eqref{eq:primal_pb}, \eqref{eq:dual_pb}, and
the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
q) \in S_1 \times S_2$, the duality primal-dual gap between the primal
LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
$a(x,y)$, can be computed as
\begin{eqnarray*}
  \begin{aligned}
    a(y,p) &= e_1^Tp +
    i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
    i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) +
    i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x' \geq
      0}{\text{max}}\text{ }x'^T(Ay - E_1^Tp) +
    \underset{q'}{\text{max}}\text{ }q'^T(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x',
      q'}{\text{max}}\text{ }x'^TAy - x^TE_1^Tp + q'^TE_2y -
    (i_{\mathbb{R}^{n_1}_+}(x') + e_2^Tq)\\
    &= g_1(y,p)
      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
      q') = g_1(y,p) -\phi_2(y,p),
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between primal LCP
\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.

@@

Consider the following algorithm
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} - \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, we have the ergodic
error bounds
\begin{eqnarray}
\|\tilde{\epsilon}^{a}_k\| \le \rho\text{ and }\|\tilde{v}^{a}_k\| \le
\epsilon, \forall k \ge 2d_0\|K\|max(5d_0/\rho, 1/\epsilon).
\end{eqnarray}
